Scheeper's Meager-NWD Game and the Menger Game

### 2014-12-04 phd/dissertation/chapter5.tex
finish chapter 5 draft

While $\pl O\ktactwin{k+1}\gruConGame{\oneptcomp X}{\infty}$ implies
$\pl O\tactwin\gruConGame{\oneptcomp X}{\infty}$, and likewise for Markov
strategies, this result cannot be
immediately extended to $\gruKPGame{X}$. However, this section will
demonstrate a non-trivial example of a space $\pmb X$ for which
$\pl K\win\gruKPGame{\pmb X}$ but $\pl K\not\kmarkwin{k}\gruKPGame{\pmb X}$
for any $k<\omega$.

\begin{thm}
  There exists a compact, zero-dimensional topological space $X$
  such that $X$ has a point-countable cover
  $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of distinct clopen sets.
\end{thm}

\begin{proof}
  (TODO)
\end{proof}

\begin{defn}
  Let $\pmb X=(X\times 2^{<\omega})\cup C$ denote a Cantor tree
  of copies of a zero-dimensional, compact space $X$ with a point-countable
  cover $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of
  clopen sets which is not $\sigma$-point-finite, along with an uncountable
  subset of the Cantor set
  $C=\{c_\alpha:\alpha<\omega_1\}\in [2^\omega]^{\omega_1}$.
  The topology on $\pmb X$ is
  given by decaring $U\times\{s\}$ to be a open
  neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
  open neighborhood $U$ of $x$ in $X$, and declaring
  $B_{\alpha,n}=(U_\alpha\times\{c_\alpha\rest n: m\leq n<\omega\})\cup\{c_\alpha\}$
  to be a clopen neighborhood of $c_\alpha\in C$ for each $\alpha<\omega_1$,
  $m<\omega$.
\end{defn}

@@

@@

% \begin{prop}
% $K \win \gruKPGame{\pmb X}$.
% \end{prop}

% \begin{thm}(cor of G, game-theoretic proof by me)
% $K\not\tactwin\gruKPGame{\pmb X}$.
% \end{thm}

% \begin{thm}
% $K\not\ktactwin{k}\gruKPGame{\pmb X}$.
% \end{thm}

>>>>

While $\pl O\ktactwin{k+1}\gruConGame{\oneptcomp X}{\infty}$ implies
$\pl O\tactwin\gruConGame{\oneptcomp X}{\infty}$, and likewise for Markov
strategies, this result cannot be
immediately extended to $\gruKPGame{X}$. However, this section will
demonstrate a non-trivial example of a locally-compact space $\pmb X$ for which
$\pl K\win\gruKPGame{\pmb X}$ but $\pl K\not\kmarkwin{k}\gruKPGame{\pmb X}$
for any $k<\omega$.

\begin{defn}
  Let $\pmb X=(X\times 2^{<\omega})\cup C$ denote a Cantor tree
  of copies of a zero-dimensional, compact space $X$ with a point-countable
  cover $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of distinct
  clopen sets, along with an uncountable subset of the Cantor set
  $C=\{c_\alpha:\alpha<\omega_1\}\in [2^\omega]^{\omega_1}$.
  The topology on $\pmb X$ is given by decaring $U\times\{s\}$ to be a open
  neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
  open neighborhood $U$ of $x$ in $X$, and declaring
  $B_{\alpha,n}=(U_\alpha\times\{c_\alpha\rest n: m\leq n<\omega\})\cup\{c_\alpha\}$
  to be a clopen neighborhood of $c_\alpha\in C$ for each $\alpha<\omega_1$,
  $m<\omega$.
\end{defn}

@@

\begin{cor}
  $\pmb X$ is $\sigma$-metacompact if and only if $\pmb X$ is metacompact.
\end{cor}

@@

Therefore if $\pmb X$ can be constructed which is not metacompact, then
$\pl K$ lacks a $k$-Markov strategy for any $k<\omega$.

\begin{thm}
  $\pmb X$ is metacompact
    if and only if
  $\{U_\alpha:\alpha<\omega_1\}$ is $\sigma$-point-finite.
\end{thm}

\begin{proof}
  Let $\omega_1=\bigcup_{n<\omega}A_n$ such that
  $\{U_\alpha:\alpha\in A_n\}$ is point-finite for each $n<\omega$.

  Let $\mc U$ be a cover of $\pmb X$, and for each $s\in 2^\omega$
  let $\mc V_s$ be a finite open refinement of $\mc C$ covering the compact
  set $X\times\{s\}$. Then let $\mc W_n = \{B_{\alpha,n_\alpha}:\alpha\in A_n\}$
  be an open refinement of $\mc C$ for each $n<\omega$, and note that it
  is point-finite. It follows that
  $\mc U' = \bigcup_{s\in 2^{<\omega}} \mc V_s \cup \bigcup_{n<\omega} \mc W_n$
  is an open $\sigma$-point-finite refinement of $\mc U$, so $\pmb X$
  is $\sigma$-metacompact, and therefore it is metacompact.

  For the other direction, consider the open cover
  $\mc U = \{B_{\alpha,0}:\alpha<\omega_1\}$ of the closed subset $C$ of
  metacompact $\pmb X$, and let $\{B_{\alpha,n_\alpha}:\alpha<\omega_1\}$ be
  a point-finite refinement. Then
  $\mc U_s = \{ U_\alpha : c_\alpha \rest n_\alpha = s\}$ is
  point-finite for $s\in 2^{<\omega}$ and
  $U_\alpha\in\mc U_{c_\alpha\rest n_\alpha}$ for each $\alpha<\omega_1$.
  Therefore $\mc U = \bigcup_{s\in 2^{<\omega}} \mc U_s$ is
  $\sigma$-point-finite.
\end{proof}

The following example was suggested by Gary Gruenhage.

\begin{thm}
  There exists a compact, zero-dimensional topological space $X$
  with a clopen cover $\{U_\alpha : \alpha<\omega_1\}$ of distinct
  sets which is not $\sigma$-point-finite.
\end{thm}

\begin{proof}
  Let $Y$ be a zero-dimensional Corson compact space which is not Eberlein
  compact; one such space was constructed in \cite{Marciszewski1991291}
  and let $X=Y^2$.
  Then by characterizations of Corson and Eberlien compacts found in
  \cite{MR752278},
  $Y^2\setminus\Delta$ is meta-Lindel\"of but not $\sigma$-metacompact, so
  there exists a point-countable clopen cover $\mc U$ of $Y^2\setminus\Delta$
  which is not $\sigma$-point-finite. Then $\mc U\cup\{X\}$ is a point-countable
  clopen cover of $X$ which is not $\sigma$-point-finite.
\end{proof}

\begin{cor}
  There exists a space $X$ such that $\pl K\win\gruKPGame{X}$ but
  $\pl K\not\kmarkwin{k} \gruKPGame{X}$ for all $k<\omega$.
\end{cor}

So the following question remains open:

\begin{ques}
  Does $\pl K\ktactwin{k+1}\gruKPGame{X}$ imply
  $\pl K\tactwin\gruKPGame{X}$ always? What about for Markov strategies?
\end{ques}
